Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-04 cav2017/cav2017.tex
intro

We propose a novel algorithm for the synthesis of control algorithms for LTI
models that are guaranteed to be 
%both \blue{stable} and 
safe, considering both the continuous dynamics of the plant and the finite-precision discrete dynamics
of the controller, as well as the hybrid elements that connect them.
%
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
%
Due to the complexity of such systems, we focus on linear models with known
implementation features (e.g., number of bits, fixed-point arithmetic). 
We~expect a safety requirement given as a reachability property.  Safety
requirements are frequently overlooked in conventional feedback control
synthesis, but play an important role in systems engineering.

@@

\todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}
%
\todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}

>>>>

We propose a novel algorithm for the synthesis of control algorithms for LTI
models that are guaranteed to be 
%both \blue{stable} and 
safe, considering both the continuous dynamics of the plant and the finite-precision discrete dynamics
of the controller, as well as the hybrid elements that connect them. 
%
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
%
We account for the presence of errors originating from a number of sources: 
quantisation errors in ADC and DAC, 
representation errors (from the discretisation introduced by finite-precision arithmetics), 
and roundoff and saturation errors in the verification process 
(from finite-precision operations).  
%
Due to the complexity of such systems, we focus on linear models with known
implementation features (e.g., number of bits, fixed-point arithmetic). 
We~expect a safety requirement given as a reachability property.  Safety
requirements are frequently overlooked in conventional feedback control
synthesis, but play an important role in systems engineering.

@@

%\todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}
%
%\todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}
